\thetitle

### 2009-02-19 paper/paper.tex
another bad "'"!
darcs-hash:20090219174744-d98fc-dbefa4cc57dc2f55b86e1d2f3bd933abbda7fc99.gz

Nondeterminism can now be emulated by instantiating these definitions with a suitable monad and |pick| operation. A deterministic, non-instrumented version can still be obtained, simply by using the identity monad and any deterministic |pick| operation, such as |head| or 'median-of-three' (not considered here).

>>>>

Nondeterminism can now be emulated by instantiating these definitions with a suitable monad and |pick| operation. A deterministic, non-instrumented version can still be obtained, simply by using the identity monad and any deterministic |pick| operation, such as |head| or `median-of-three' (not considered here).
